Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-03-09 docs/manuscript/manuscript.tex
Updates from Overleaf

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Advanced Correlation Graph of Water Variables}
  \label{fig:cor-plot}
\end{figure}
Next, we studied the explanatory variables that we collected and extracted from the World Bank Data.

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{adv-cor-plot}
  \caption{Advanced Correlation Graph of Water Variables}
  \label{fig:cor-plot}
\end{figure}
Next, we studied the explanatory variables that we collected and extracted from the World Bank Data. Then we developed an advanced correlation graph to quickly analyze the relationships between the eight variables previously mentioned in \autoref{tab:summary-var}. Total adult literacy rate and youth literacy rate (ages 15-24) has the strongest correlation of .97 and p-value of less than 0.001 which are summarized with three asterisks in \autoref{fig:cor-wb}. GDP (current US Currency) and Total Population has the second strongest correlation of .95 and p-value of less than .001 in \autoref{fig:cor-wb}. These explanatory variables will assist in finding results in the classification of which explanatory variables may affect the improvement of the water accessibility variables.
